Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
separated weaknesses into its own section

To forecast the 2024 United States presidential election, a generalized linear model and a Bayesian model were built. These models will help us predict who will win the election based on the electoral college system. An important finding from our model is that we predict Kamala Harris wins the presidential election with 279 electoral college votes. This would be a historic win, as she would be the first woman to become US president, a significant milestone in American politics. One drawback of our model stems from the representativeness of the dataset, as it does not include all 50 states in the polls, which may impact the electoral college votes. More is discussed in @sec-disc-imp.

@@

## Implications and Potential Weaknesses {#sec-disc-imp}

@@

@@

Our model does not take into account state correlations based on past election data and research-based insights into voter preference. For example, a model developed by Chernov, Elenev, and Song, posits if Harris were to win Pennsylvania, then her chances of winning Nevada would increase from 24% to 68% [https://anderson-review.ucla.edu/wp-content/uploads/2024/10/voter_preferences_updated.pdf]. These correlations between states could have a large impact on election predictions and our model is limited by not modeling these interactions.

>>>>

To forecast the 2024 United States presidential election, a generalized linear model and a Bayesian model were built. These models will help us predict who will win the election based on the electoral college system. An important finding from our model is that we predict Kamala Harris wins the presidential election with 279 electoral college votes. This would be a historic win, as she would be the first woman to become US president, a significant milestone in American politics. One drawback of our model stems from the representativeness of the dataset, as it does not include all 50 states in the polls, which may impact the electoral college votes. More is discussed in @sec-disc-weaknesses.

@@

## Result Implications {#sec-disc-imp}

@@

## Potential Weaknesses {#sec-disc-weaknesses}

@@

Our model does not take into account state correlations based on past election data and research-based insights into voter preference. For example, a model developed by Chernov, Elenev, and Song, posits if Harris were to win Pennsylvania, then her chances of winning Nevada would increase from 24% to 68% [@market_paper]. These correlations between states could have a large impact on election predictions and our model is limited by not modeling these interactions.
